Spatial Reasoning and Data Displays

### 2015-06-26 Paper/InfoVis2015Revision/ResponsesToReviewers.Rmd

We would like to thank the reviewers for the detailed comments. We hope to have addressed all of the questions.

We are detailing our response below:

# Major Concerns
1. **Are all the experimental design choices properly motivated?**    
**(refer to the first concern of R1).**

*We have extended the discussion of the choice of cognitive tests; the purpose of each of the cognitive tests is described in section 2.2. In summary, the paper-folding, card rotation, and figure classification tasks are part of the kit of factor-referenced cognitive tests (and are thus extremely well-studied); additionally, we included a visual searching task (VST) because of its similarity of form to statistical lineups and its' compatibility with the written form of the other cognitive tests and lineup tests.*    
*As mentioned in the paper, the paper folding and card rotation tests have been used in many previous studies of statistical graphics and data displays. The figure-classification task examines inductive reasoning, which is another component of the lineup task (determining the dimension on which the lineup components differ, then applying that to answer the question successfully).*
*Regarding our hypotheses about the relationship of the visuospatial tests and lineups: we extended the discussion in the introduction; in summary we hypothesize that visual search is the basis for any lineup evaluation. We are further intrested in whether the spatial component (measured in 2d by the card rotation test or in 3d by the paper folding test) dominates lineup performance or inductive reasoning (as measured by the figure classification test).*

### 2015-06-26 Paper/InfoVis2015Revision/ResponsesToReviewers.Rmd

---
title: "Summary of Changes"
author: "Susan VanderPlas & Heike Hofmann"
output: word_document
---

We would like to thank the reviewers for the detailed comments. We hope to have addressed all of the questions.

We are detailing our response below:

# Major Concerns
1. **Are all the experimental design choices properly motivated?**    
**(refer to the first concern of R1).**    
*We have extended the discussion of the choice of cognitive tests; the purpose of each of the cognitive tests is described in section 2.2. In summary, the paper-folding, card rotation, and figure classification tasks are part of the kit of factor-referenced cognitive tests (and are thus extremely well-studied); additionally, we included a visual searching task (VST) because of its similarity of form to statistical lineups and its' compatibility with the written form of the other cognitive tests and lineup tests.*    
*As mentioned in the paper, the paper folding and card rotation tests have been used in many previous studies of statistical graphics and data displays. The figure-classification task examines inductive reasoning, which is another component of the lineup task (determining the dimension on which the lineup components differ, then applying that to answer the question successfully).*
*Regarding our hypotheses about the relationship of the visuospatial tests and lineups: we extended the discussion in the introduction; in summary we hypothesize that visual search is the basis for any lineup evaluation. We are further intrested in whether the spatial component (measured in 2d by the card rotation test or in 3d by the paper folding test) dominates lineup performance or inductive reasoning (as measured by the figure classification test).*

### 2015-06-26 Paper/InfoVis2015Revision/TestingVisualAptitude.Rnw
Saving space

Assume that an observer has evaluated $K$ lineups of size $m$ (consisting of $m-1$ decoy plots and 1 target), and successfully identified the target in $n_c$ of these plots, while missing the target in $n_w$ of them. 
The score for this individual is then given as:
\begin{eqnarray}\label{eq.scoring1}
n_c - \textstyle\frac{n_w}{m-1}.
\end{eqnarray}
Note that the sum of answers, $n_c + n_w$, is at most $K$, but may be less, if an observer chooses to not answer one of the lineup tasks or runs out of time.

The scoring scheme as given in (\ref{eq.scoring1}) is chosen so that if participants are guessing, the expected score is 0.

@@

\paragraph{Lineup Set 1}
The lineups in this set are taken from an experiment which examined the use of boxplots, density plots, histograms, and dotplots to compare two groups which vary in mean and sample size. This set of lineups consists of 20 plots selected from the plots used in the full experiment; each set of data is displayed with each of the four plot types. Figure \ref{fig:lineups} (a)-(d) provides an example of the four plot types displaying the same data.

@@

\begin{table*}[htb]\centering
\begin{tabular}{rlllc}
\hline
  & Card Rotation & Paper Folding & Figure Classification & Visual Search  \\\hline
ISU Students & \Sexpr{round(mean(ans.summary$card_rot), 1)} (\Sexpr{round(sd(ans.summary$card_rot), 1)}) 
             & \Sexpr{round(mean(ans.summary$folding), 1)} (\Sexpr{round(sd(ans.summary$folding), 1)})
             & \Sexpr{sprintf("%.1f", mean(ans.summary$fig_class))} (\Sexpr{round(sd(ans.summary$fig_class), 1)})\footnotemark[1]
             & \Sexpr{round(mean(ans.summary$vis_search), 1)} (\Sexpr{round(sd(ans.summary$vis_search), 1)})\\
Scaled Scores & 88.0 (\Sexpr{round(sqrt((24.6^2)*2), 1)})
              & 13.8 (4.5)
              & \Sexpr{round((120.0*294 + 114.9*323)/617/2, 1)} (\Sexpr{round(sqrt((30^2*294 + 27.8^2*323)/617)/2, 1)})\footnotemark[2]
              & -- \\
Unscaled Scores & 44.0 (24.6)\footnotemark[3]
                & 13.8 (4.5)
                & \parbox[c]{.2\linewidth}{M:~120.0~(30.0)\\ F:~114.9~(27.8)}
                & --\\\hline
{\footnotesize Population}    
              & \parbox[t]{.15\linewidth}{\footnotesize approx.\ 550 male\\ naval recruits} 
              & \parbox[t]{.17\linewidth}{\footnotesize 46 college students\\(1963~version)}
              & \parbox[t]{.2\linewidth}{\footnotesize suburban 11th \& 12th \\ grade students\\(288-300 M, 317-329 F)}
              & \\\hline
\end{tabular}
\caption[Comparison of scores for cognitive tasks.]{Comparison of scores from Iowa State students and scores reported in~\protect~\cite{ekstrom1976manual}. Scaled scores are calculated based on information reported in the manual, scaled to account for differences in the number of questions answered during this experiment. Data shown are from the population most similar to ISU students, out of the data available. The visual search task~\protect~\cite{goldstein1973validity,demita1981validity,moerland1986neuropsychological} is not part of the Kit of Factor Referenced Cognitive Test data, and thus we do not have comparison data for the form used in this experiment.
\label{tab:scorecomparison}}
\end{table*}

@@

<<pcarotation4,echo=F, results='asis'>>=
row.names(pca2$rotation) <- c("Card Rot", "Fig Class", "Folding", "VST")
print(xtable(pca2$rotation, caption="Rotation matrix for principal component analysis of the four cognitive tests (visual search, paper folding, card rotation, figure classification).\\label{tab:PCArotation4}",digits=2), sanitize.text.function=sanitize, sanitize.rownames.function=sanitize, sanitize.colnames.function=sanitize, table.placement="htb", caption.placement="top")
@

@@

<<pcarotation5,echo=F, results='asis'>>=
print(xtable(pca$rotation, caption="PCA Rotation matrix for all five tests. The first principal component is essentially an average of all five tests. 
             \\label{tab:PCArotation5}",digits=2), sanitize.text.function=sanitize, sanitize.rownames.function=sanitize, sanitize.colnames.function=sanitize, table.placement="ht", caption.placement="top")
@
From the rotation matrix (see Table~\ref{tab:PCArotation5}) we see that  
the first principal component, PC1, is again essentially an average across all tests and accounts for \Sexpr{round(summary(pca)$importance[3,1]*100,1)}\% of the variance in the data.

>>>>

Assume that an observer has evaluated $K$ lineups of size $m$ (consisting of $m-1$ decoy plots and 1 target), and successfully identified the target in $n_c$ of these plots, while missing the target in $n_w$ of them. 
The score for this individual is then given as:
\begin{equation}\label{eq.scoring1}
n_c - n_w/(m-1)
\end{equation}
Note that the sum of answers, $n_c + n_w$, is at most $K$, but may be less, if an observer chooses to not answer one of the lineup tasks or runs out of time. The scoring scheme as given in (\ref{eq.scoring1}) is chosen so that if participants are guessing, the expected score is 0.

@@

\begin{table*}[htbp]\centering
\begin{tabular}{rlllc}
\hline
  & Card Rotation & Paper Folding & Figure Classification & Visual Search  \\\hline
ISU Students & \Sexpr{round(mean(ans.summary$card_rot), 1)} (\Sexpr{round(sd(ans.summary$card_rot), 1)}) 
             & \Sexpr{round(mean(ans.summary$folding), 1)} (\Sexpr{round(sd(ans.summary$folding), 1)})
             & \Sexpr{sprintf("%.1f", mean(ans.summary$fig_class))} (\Sexpr{round(sd(ans.summary$fig_class), 1)})\footnotemark[1]
             & \Sexpr{round(mean(ans.summary$vis_search), 1)} (\Sexpr{round(sd(ans.summary$vis_search), 1)})\\
Scaled Scores & 88.0 (\Sexpr{round(sqrt((24.6^2)*2), 1)})
              & 13.8 (4.5)
              & \Sexpr{round((120.0*294 + 114.9*323)/617/2, 1)} (\Sexpr{round(sqrt((30^2*294 + 27.8^2*323)/617)/2, 1)})\footnotemark[2]
              & -- \\
Unscaled Scores & 44.0 (24.6)\footnotemark[3]
                & 13.8 (4.5)
                & \parbox[c]{.2\linewidth}{M:~120.0~(30.0)\\ F:~114.9~(27.8)}
                & --\\\hline
{\footnotesize Population}    
              & \parbox[t]{.15\linewidth}{\footnotesize approx.\ 550 male\\ naval recruits} 
              & \parbox[t]{.17\linewidth}{\footnotesize 46 college students\\(1963~version)}
              & \parbox[t]{.2\linewidth}{\footnotesize suburban 11th \& 12th \\ grade students\\(288-300 M, 317-329 F)}
              & \\\hline
\end{tabular}
\caption[Comparison of scores for cognitive tasks.]{Comparison of scores from Iowa State students and scores reported in~\protect~\cite{ekstrom1976manual}. Scaled scores are calculated based on information reported in the manual, scaled to account for differences in the number of questions answered during this experiment. Data shown are from the population most similar to ISU students, out of the data available. The visual search task~\protect~\cite{goldstein1973validity,demita1981validity,moerland1986neuropsychological} is not part of the Kit of Factor Referenced Cognitive Test data, and thus we do not have comparison data for the form used in this experiment.
\label{tab:scorecomparison}}
\end{table*}

\paragraph{Lineup Set 1}
The lineups in this set are taken from an experiment which examined the use of boxplots, density plots, histograms, and dotplots to compare two groups which vary in mean and sample size. This set of lineups consists of 20 plots selected from the plots used in the full experiment; each set of data is displayed with each of the four plot types. Figure \ref{fig:lineups} (a)-(d) provides an example of the four plot types displaying the same data.\hphantom{\ref{tab:scorecomparison}}

@@

@@

<<pcarotation4,echo=F, results='asis'>>=
row.names(pca2$rotation) <- c("Card Rot", "Fig Class", "Folding", "VST")
print(xtable(pca2$rotation, caption="Rotation matrix for principal component analysis of the four cognitive tests (visual search, paper folding, card rotation, figure classification).\\label{tab:PCArotation4}",digits=2), sanitize.text.function=sanitize, sanitize.rownames.function=sanitize, sanitize.colnames.function=sanitize, size="footnotesize", table.placement="htb", caption.placement="top")
@

@@

<<pcarotation5,echo=F, results='asis'>>=
row.names(pca$rotation) <- c("Lineup", "Card Rot", "Fig Class", "Folding", "VST")
print(
  xtable(
    pca$rotation, 
    caption="PCA Rotation matrix for all five tests. The first principal component is essentially an average of performance on all five tests. \\label{tab:PCArotation5}", 
    digits=2), 
  sanitize.text.function=sanitize, 
  sanitize.rownames.function=sanitize, 
  sanitize.colnames.function=sanitize, 
  table.placement="ht", caption.placement="top")
@
From the rotation matrix (see Table~\ref{tab:PCArotation5}) we see that  
the first principal component, PC1, is again essentially an average across all tests and accounts for \Sexpr{round(summary(pca)$importance[3,1]*100,1)}\% of the variance in the data.

### 2015-06-26 Paper/InfoVis2015Revision/TestingVisualAptitude.tex
response, better formulated for hypothesis of relationship
Saving space

\paragraph{Lineup Set 1}
The lineups in this set are taken from an experiment which examined the use of boxplots, density plots, histograms, and dotplots to compare two groups which vary in mean and sample size. This set of lineups consists of 20 plots selected from the plots used in the full experiment; each set of data is displayed with each of the four plot types. Figure \ref{fig:lineups} (a)-(d) provides an example of the four plot types displaying the same data.

@@

\begin{table*}[htb]\centering
\begin{tabular}{rlllc}
\hline
  & Card Rotation & Paper Folding & Figure Classification & Visual Search  \\\hline
ISU Students & 83.4 (24.1) 
             & 12.4 (3.7)
             & 57.0 (23.8)\footnotemark[1]
             & 21.9 (2.3)\\
Scaled Scores & 88.0 (34.8)
              & 13.8 (4.5)
              & 58.7 (14.4)\footnotemark[2]
              & -- \\
Unscaled Scores & 44.0 (24.6)\footnotemark[3]
                & 13.8 (4.5)
                & \parbox[c]{.2\linewidth}{M:~120.0~(30.0)\\ F:~114.9~(27.8)}
                & --\\\hline
{\footnotesize Population}    
              & \parbox[t]{.15\linewidth}{\footnotesize approx.\ 550 male\\ naval recruits} 
              & \parbox[t]{.17\linewidth}{\footnotesize 46 college students\\(1963~version)}
              & \parbox[t]{.2\linewidth}{\footnotesize suburban 11th \& 12th \\ grade students\\(288-300 M, 317-329 F)}
              & \\\hline
\end{tabular}
\caption[Comparison of scores for cognitive tasks.]{Comparison of scores from Iowa State students and scores reported in~\protect~\cite{ekstrom1976manual}. Scaled scores are calculated based on information reported in the manual, scaled to account for differences in the number of questions answered during this experiment. Data shown are from the population most similar to ISU students, out of the data available. The visual search task~\protect~\cite{goldstein1973validity,demita1981validity,moerland1986neuropsychological} is not part of the Kit of Factor Referenced Cognitive Test data, and thus we do not have comparison data for the form used in this experiment.
\label{tab:scorecomparison}}
\end{table*}

@@

% latex table generated in R 3.1.1 by xtable 1.7-3 package
% Fri Jun 26 14:46:58 2015
\begin{table}[htb]
\centering
\caption{Importance of principal components in an analysis of four tests of spatial ability: figure classification, paper folding, card rotation, and visual search.\label{tab:PCAvariance4}} 
{\footnotesize
\begin{tabular}{rrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 \\ 
  \hline
Standard deviation & 1.61 & 0.81 & 0.73 & 0.49 \\ 
  Proportion of Variance & 0.64 & 0.16 & 0.13 & 0.06 \\ 
  Cumulative Proportion & 0.64 & 0.81 & 0.94 & 1.00 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

% latex table generated in R 3.1.1 by xtable 1.7-3 package
% Fri Jun 26 14:46:59 2015
\begin{table}[htb]
\centering
\caption{Rotation matrix for principal component analysis of the four cognitive tests (visual search, paper folding, card rotation, figure classification).\label{tab:PCArotation4}} 
\begin{tabular}{rrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 \\ 
  \hline
Card Rot & 0.55 & -0.19 & -0.38 & 0.72 \\ 
  Fig Class & 0.46 & 0.58 & 0.66 & 0.14 \\ 
  Folding & 0.52 & 0.33 & -0.53 & -0.59 \\ 
  VST & 0.46 & -0.72 & 0.38 & -0.34 \\ 
   \hline
\end{tabular}
\end{table}

@@

Next, we add the lineup results to our principal components analysis. The results of the principal component analysis of the four cognitive tests and lineup results are similar to the results of the cognitive tests alone; this suggests that lineups require at least some of the skills measured by the other cognitive tests. Table~\ref{tab:PCAvariance5} shows the importance of each principal component; from the distribution of the variance components, we see that the lineup test spans an additional dimension within the space of the four established tests. 
% latex table generated in R 3.1.1 by xtable 1.7-3 package
% Fri Jun 26 14:46:59 2015
\begin{table}[ht]
\centering
\caption{Importance of principal components, analyzing all five tests.\label{tab:PCAvariance5}} 
{\footnotesize
\begin{tabular}{rrrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 & PC5 \\ 
  \hline
Standard deviation & 1.73 & 0.84 & 0.75 & 0.70 & 0.48 \\ 
  Proportion of Variance & 0.60 & 0.14 & 0.11 & 0.10 & 0.05 \\ 
  Cumulative Proportion & 0.60 & 0.74 & 0.85 & 0.95 & 1.00 \\ 
   \hline
\end{tabular}
}
\end{table}

% latex table generated in R 3.1.1 by xtable 1.7-3 package
% Fri Jun 26 14:46:59 2015
\begin{table}[ht]
\centering
\caption{PCA Rotation matrix for all five tests. The first principal component is essentially an average of all five tests. 
             \label{tab:PCArotation5}} 
\begin{tabular}{rrrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 & PC5 \\ 
  \hline
lineup & 0.42 & 0.49 & -0.46 & 0.60 & -0.10 \\ 
  card.rot & 0.50 & -0.30 & 0.28 & 0.23 & 0.73 \\ 
  fig.class & 0.43 & 0.45 & -0.15 & -0.75 & 0.18 \\ 
  folding & 0.47 & 0.07 & 0.68 & 0.04 & -0.56 \\ 
  vis.search & 0.41 & -0.69 & -0.48 & -0.15 & -0.33 \\ 
   \hline
\end{tabular}
\end{table}

@@

% latex table generated in R 3.1.1 by xtable 1.7-3 package
% Fri Jun 26 14:46:59 2015
\begin{table}[ht]
\centering
\caption{Estimates and significances of a linear model of lineup scores.} 
\label{tab:m1}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 14.1192 & 1.9149 & 7.37 & 0.0000 \\ 
  PC1 & 1.7672 & 0.5230 & 3.38 & 0.0018 \\ 
  MATH & 2.1246 & 0.8732 & 2.43 & 0.0202 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\begin{table*}[htbp]\centering
\begin{tabular}{rlllc}
\hline
  & Card Rotation & Paper Folding & Figure Classification & Visual Search  \\\hline
ISU Students & 83.4 (24.1) 
             & 12.4 (3.7)
             & 57.0 (23.8)\footnotemark[1]
             & 21.9 (2.3)\\
Scaled Scores & 88.0 (34.8)
              & 13.8 (4.5)
              & 58.7 (14.4)\footnotemark[2]
              & -- \\
Unscaled Scores & 44.0 (24.6)\footnotemark[3]
                & 13.8 (4.5)
                & \parbox[c]{.2\linewidth}{M:~120.0~(30.0)\\ F:~114.9~(27.8)}
                & --\\\hline
{\footnotesize Population}    
              & \parbox[t]{.15\linewidth}{\footnotesize approx.\ 550 male\\ naval recruits} 
              & \parbox[t]{.17\linewidth}{\footnotesize 46 college students\\(1963~version)}
              & \parbox[t]{.2\linewidth}{\footnotesize suburban 11th \& 12th \\ grade students\\(288-300 M, 317-329 F)}
              & \\\hline
\end{tabular}
\caption[Comparison of scores for cognitive tasks.]{Comparison of scores from Iowa State students and scores reported in~\protect~\cite{ekstrom1976manual}. Scaled scores are calculated based on information reported in the manual, scaled to account for differences in the number of questions answered during this experiment. Data shown are from the population most similar to ISU students, out of the data available. The visual search task~\protect~\cite{goldstein1973validity,demita1981validity,moerland1986neuropsychological} is not part of the Kit of Factor Referenced Cognitive Test data, and thus we do not have comparison data for the form used in this experiment.
\label{tab:scorecomparison}}
\end{table*}

\paragraph{Lineup Set 1}
The lineups in this set are taken from an experiment which examined the use of boxplots, density plots, histograms, and dotplots to compare two groups which vary in mean and sample size. This set of lineups consists of 20 plots selected from the plots used in the full experiment; each set of data is displayed with each of the four plot types. Figure \ref{fig:lineups} (a)-(d) provides an example of the four plot types displaying the same data.\hphantom{\ref{tab:scorecomparison}}

@@

@@

% latex table generated in R 3.2.1 by xtable 1.7-1 package
% Fri Jun 26 12:42:40 2015
\begin{table}[htb]
\centering
\caption{Importance of principal components in an analysis of four tests of spatial ability: figure classification, paper folding, card rotation, and visual search.\label{tab:PCAvariance4}} 
{\footnotesize
\begin{tabular}{rrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 \\ 
  \hline
Standard deviation & 1.61 & 0.81 & 0.73 & 0.49 \\ 
  Proportion of Variance & 0.64 & 0.16 & 0.13 & 0.06 \\ 
  Cumulative Proportion & 0.64 & 0.81 & 0.94 & 1.00 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

% latex table generated in R 3.2.1 by xtable 1.7-1 package
% Fri Jun 26 12:42:40 2015
\begin{table}[htb]
\centering
\caption{Rotation matrix for principal component analysis of the four cognitive tests (visual search, paper folding, card rotation, figure classification).\label{tab:PCArotation4}} 
{\footnotesize
\begin{tabular}{rrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 \\ 
  \hline
Card Rot & 0.55 & -0.19 & -0.38 & 0.72 \\ 
  Fig Class & 0.46 & 0.58 & 0.66 & 0.14 \\ 
  Folding & 0.52 & 0.33 & -0.53 & -0.59 \\ 
  VST & 0.46 & -0.72 & 0.38 & -0.34 \\ 
   \hline
\end{tabular}
}
\end{table}

@@

Next, we add the lineup results to our principal components analysis. The results of the principal component analysis of the four cognitive tests and lineup results are similar to the results of the cognitive tests alone; this suggests that lineups require at least some of the skills measured by the other cognitive tests. Table~\ref{tab:PCAvariance5} shows the importance of each principal component; from the distribution of the variance components, we see that the lineup test spans an additional dimension within the space of the four established tests. 
% latex table generated in R 3.2.1 by xtable 1.7-1 package
% Fri Jun 26 12:42:40 2015
\begin{table}[ht]
\centering
\caption{Importance of principal components, analyzing all five tests.\label{tab:PCAvariance5}} 
{\footnotesize
\begin{tabular}{rrrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 & PC5 \\ 
  \hline
Standard deviation & 1.73 & 0.84 & 0.75 & 0.70 & 0.48 \\ 
  Proportion of Variance & 0.60 & 0.14 & 0.11 & 0.10 & 0.05 \\ 
  Cumulative Proportion & 0.60 & 0.74 & 0.85 & 0.95 & 1.00 \\ 
   \hline
\end{tabular}
}
\end{table}

% latex table generated in R 3.2.1 by xtable 1.7-1 package
% Fri Jun 26 12:42:40 2015
\begin{table}[ht]
\centering
\caption{PCA Rotation matrix for all five tests. The first principal component is essentially an average of performance on all five tests. \label{tab:PCArotation5}} 
\begin{tabular}{rrrrrr}
  \hline
 & PC1 & PC2 & PC3 & PC4 & PC5 \\ 
  \hline
Lineup & 0.42 & 0.49 & -0.46 & 0.60 & -0.10 \\ 
  Card Rot & 0.50 & -0.30 & 0.28 & 0.23 & 0.73 \\ 
  Fig Class & 0.43 & 0.45 & -0.15 & -0.75 & 0.18 \\ 
  Folding & 0.47 & 0.07 & 0.68 & 0.04 & -0.56 \\ 
  VST & 0.41 & -0.69 & -0.48 & -0.15 & -0.33 \\ 
   \hline
\end{tabular}
\end{table}

@@

% latex table generated in R 3.2.1 by xtable 1.7-1 package
% Fri Jun 26 12:42:41 2015
\begin{table}[ht]
\centering
\caption{Estimates and significances of a linear model of lineup scores.} 
\label{tab:m1}
\begin{tabular}{rrrrr}
  \hline
 & Estimate & Std. Error & t value & Pr($>$$|$t$|$) \\ 
  \hline
(Intercept) & 14.1192 & 1.9149 & 7.37 & 0.0000 \\ 
  PC1 & 1.7672 & 0.5230 & 3.38 & 0.0018 \\ 
  MATH & 2.1246 & 0.8732 & 2.43 & 0.0202 \\ 
   \hline
\end{tabular}
\end{table}
